cool so see % Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{xcolor}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.9in}
\addtolength{\textheight}{1.8in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=-2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    {\Huge \scshape Mrityunjay Raj} \\ \vspace{4pt}
    \small 
    \href{tel:+919304584358}{\faPhone\ +91 930 458 4358} ~ 
    \href{mailto:mr.raj.earth@gmail.com}{\faEnvelope\ \underline{mr.raj.earth@gmail.com}} ~
    \href{https://www.linkedin.com/in/mrityunjay-raj-75808b1b6/}{\faLinkedin\ \underline{LinkedIn}} ~
    \href{https://codeforces.com/profile/mr_raj12}{\faKeyboard\ \underline{Codeforces}} ~
    \href{https://leetcode.com/mr_raj12}{\faLaptopCode\ \underline{LeetCode}} ~
    \href{https://github.com/mr-raj12}{\faGithub\ \underline{GitHub}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Birla Institute of Technology, Mesra}{Sept 2023 -- Jul 2027}
      {Bachelor of Technology in Computer Science $|$ CGPA: 8.22}{Ranchi, Jharkhand}
    \resumeSubheading
      {Darbhanga Public School}{Aug 2020 -- Jun 2022}
      {\textbf{PCM} (12th: 91.0\%)}{Darbhanga, Bihar}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Open Source Contributor} $|$ \textmd{BorgBase, BorgBackup, AboutCode \& OSSF}}{Dec 2025 -- Present}
      {60+ Pull Requests}{Remote}
      \resumeItemListStart
        \resumeItem{\textbf{BorgBackup (Borg):} Authored 33 PRs optimizing CI/CD pipelines, Python 3.12 compatibility, and resolving complex timezone bugs and solving several major bugs. \hspace*{\fill} \href{https://github.com/}{\textbf{[Link]}}}
        \resumeItem{\textbf{BorgBase (Vorta):} Authored 16 PRs optimizing CI/CD pipelines, Python 3.12 compatibility, and resolving complex timezone bugs along with completing 2 projects. \hspace*{\fill} \href{https://github.com/}{\textbf{[Link]}}}
        \resumeItem{\textbf{AboutCode:} Submitted 16 PRs across ScanCode \& VulnerableCode enhancing code quality and CI workflows. \hspace*{\fill} \href{https://github.com/}{\textbf{[Link]}}}
        \resumeItem{\textbf{OSSF (CVE Binary Tool):} Resolved critical Windows crash loops involving sqlite3 databases via filesystem optimizations. \hspace*{\fill} \href{https://github.com/}{\textbf{[Link]}}}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{EkamApps (Turrant AI)} $|$ \textmd{Python, PostgreSQL, REST APIs, Next.js}}{Oct 2025 -- Jan 2026}
      {AI Engineering Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Engineered a scalable RESTful API suite and credit-based billing microservice, successfully handling 500+ concurrent transactions using Node.js.}
        \resumeItem{Architected a multi-tenant notification system across WhatsApp, email, and web portals using an event-driven architecture.}
        \resumeItem{Optimized PostgreSQL schemas (118+ tables) via advanced query tuning and indexing, improving OCR accuracy by 25\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{PromptCue} $|$ \textmd{Node.js, Next.js, Redis}}{Dec 2024 -- Jun 2025}
      {SDE Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Built an AI aggregator platform integrating LLMs, MCP tools, local file systems, and image generation APIs using Node.js and Next.js.}
        \resumeItem{Reduced model inference latency by 30\% by implementing Redis caching strategies and asynchronous processing queues.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS---------------
\section{Achievements}
    \begin{itemize}[itemsep=-2pt, parsep=3pt, leftmargin=0.15in]
        \small
        \item Served as \textbf{Technical Lead} for \textbf{Pantheon'25}, managing infrastructure for 4000+ visitors and spearheading the 'HackQuest'25' hackathon for 1200+ participants. \hspace*{\fill} \href{https://github.com/}{\textbf{[Link]}}
        \item Acted as \textbf{Core Developer} for \textbf{BITOTSAV}, building a QR-based ticketing system for 5000+ attendees and boosting engagement by 40\%. \hspace*{\fill} \href{https://github.com/}{\textbf{[Link]}}
        \item Served as \textbf{Technical Coordinator} for \textbf{UNESQUO \& SPIC MACAY}, ensuring 99.9\% uptime for web platforms during cultural events. \hspace*{\fill} \href{https://github.com/}{\textbf{[Link]}}
        \item Secured \textbf{2nd place} for an innovative Stocks Portfolio Manager solution in \textbf{HACKATRON} at BIT Sindri. \hspace*{\fill} \href{https://github.com/}{\textbf{[Link]}}
        \item Received Pre-Placement Interview (PPI) from ILNB Services in \textbf{HACKFEST} by \textbf{IIT ISM Dhanbad}. \hspace*{\fill} \href{https://github.com/}{\textbf{[Credential]}}
        \item Secured \textbf{1st place} in \textbf{CICADA-CTF} and won the no-monitor contest in \textbf{Blind Coding}. \hspace*{\fill} \href{https://github.com/}{\textbf{[Certificate]}}
    \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Gsoc-espionage} $|$ \emph{React.js, TypeScript, Vite, GitHub REST API}}{\href{https://gsoc-espionage.vercel.app/}{\textbf{Live}} $|$ \href{https://github.com/mr-raj12}{\textbf{GitHub}}}
      \resumeItemListStart
        \resumeItem{Engineered a GitHub PR analytics dashboard serving \textbf{1.4k active users}, visualizing merge rates, contributor stats, and activity timelines for any repository via the GitHub API.}
        \resumeItem{Implemented advanced data handling features including branch filtering, customizable time ranges, and \textbf{CSV/JSON data exports} for detailed repository auditing.}
        \resumeItem{Integrated dynamic \textbf{GSoC 2026 organization lists} and robust theme support, ensuring a highly scalable and accessible user experience.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} C, C++, Java, Python, JavaScript, TypeScript, HTML/CSS, SQL, Solidity \\ \vspace{2pt}
     \textbf{Web Technologies:} Next.js, Node.js, GraphQL, REST APIs, WebSockets, Prisma, Supabase, Appwrite \\ \vspace{2pt}
     \textbf{Databases \& Cloud:} PostgreSQL, MongoDB, Redis, Docker, AWS, GCP, Nginx, CI/CD \\ \vspace{2pt}
     \textbf{Developer Tools:} Git, GitHub, VS Code, Postman, Firebase, Vercel, Cloudinary, Render
    }}
 \end{itemize}

\end{document}  
